Summary Tables

### 2019-04-09 summary_tables.Rmd
Add opts chunk param

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadLibraries, echo = F}
library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
```

@@

for(city in cities){
    td <- io[[city]]$dur
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}
```

```{r pa="asis"}

for (city in cities){
  td <- io[[city]]$outcomes$mmets %>% dplyr::select(-c(participant_id))
  print(summarytools::dfSummary(td))
  cat("\n")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')

```{r loadLibraries, echo = F}
library(summarytools)
library(knitr)
library(summarytools)
#library(tidyverse)

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

@@

for(city in cities){
    td <- io[[city]]$dur
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}

```{r pa = "asis"}

for (city in cities){
  td <- io[[city]]$outcomes$mmets
  print(dfSummary(td))
  cat("\n")
